An analysis of PCA image reconstruction for classification

### 2010-04-13 paper/paper.tex
Adição das tabelas.

% TODO Table comparing AUCs
% K GRAY  EDGE  TOTAL
% 400 0.9611  0.9863  0.9744
% 300 0.9694  0.9877  0.9826
% 200 0.9768  0.9905  0.9877
% 100 0.9851  0.9944  0.9948
% 50  0.9905  0.9956  0.9972
% 25  0.9929  0.9913  0.9984

@@

@@

The dimensions affect not in a linear way, e.g., the more the better is wrong.

@@

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...
more thanks here

>>>>

\begin{table}
  \caption{Comparison of area under the curve (AUC) of the classifiers based on grayscale error, edge error, and total error, respectively, for many values of $k$. The AUCs of the edge-based classifier are always larger then the grayscale-based classifier. This indicates edge errors are more relevant to the classification.}
  \begin{center}
    \begin{tabular}{  c | c  c  c  }
      \hline
      $k$ & Gray & Edge & Total \\
      \hline
      400 & 0.9611 & 0.9863 & 0.9744 \\
      300 & 0.9694 & 0.9877 & 0.9826 \\ 
      200 & 0.9768 & 0.9905 & 0.9877 \\
      100 & 0.9851 & 0.9944 & 0.9948 \\
      50  & 0.9905 & 0.9956 & 0.9972 \\
      25  & 0.9929 & 0.9913 & 0.9984 \\
      \hline  
    \end{tabular}
  \end{center}
  \label{table-gray-vs-edge}
\end{table}

@@

\begin{table}
  \caption{Weights that produced best classification rates for each value of $k$. Note that the weights associated to edge errors are usually larger than the errors associated to grayscale errors, what reinforces the greater importance of the edge errors to the classification.}
  \begin{center}
    \begin{tabular}{  c | c  c  c  c  }
      \hline
      $k$ & $w_{gp}$ & $w_{ep}$ & $w_{gn}$ & $w_{en}$ \\
      \hline
      400 & 0.4456 & 0.5472 & 0.2785 & 0.9340 \\
      300 & 1.6523 & 0.7827 & 0.9183 & 2.2065 \\
      200 & 0.3101 & 0.6551 & 0.1338 & 0.9962 \\
      100 & 0.8472 & 1.3322 & 0.7671 & 1.5308 \\
      50  & 0.2236 & 0.8294 & 0.1905 & 0.9043 \\
      25  & 0.9172 & 1.1696 & 0.7768 & 1.4662 \\
      \hline  
    \end{tabular}
  \end{center}
  \label{table-weights}
\end{table}

@@

% The dimensions affect not in a linear way, e.g., the more the better is wrong.

@@

% use section* for acknowledgement
% \section*{Acknowledgment}
% 
% 
% The authors would like to thank...
% more thanks here
